---
title: "Practical Exam"
author: "Abdul Azim P. Bansara"
date: "2024-03-06"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1A. Find out, in a single command, which columns of warpbreaks are either numeric or
integer. What are the data types of each column?
```{r}
data("warpbreaks")

#the coloumn breaks are numeric 
```

2A. How many observations does it have?
```{r}
str(warpbreaks)

#there are 54 observation

```
3A. Is numeric a natural data type for the columns which are stored as such? Convert to
integer when necessary.
```{r, error=TRUE}
intwarpbreaks <- warpbreaks

intwarpbreaks <- as.integer(warpbreaks)

#intwarpbreaks <- as.integer(warpbreaks$breaks)
#intwarpbreaks <- as.integer(warpbreaks$wool)
#intwarpbreaks <- as.integer(warpbreaks$tension)
```

4A.Error messages in R sometimes report the underlying type of an object rather than the
user-level class. Derive from the following code and error message what the
underlying type. Explain what is the error all about. Do not just copy the error
message that was displayed.
```{r}
# it is error because it cannot forced to convert the list of object in data  to integer.


```

B. Load the exampleFile.txt

1B.Read the complete file using readLines.
```{r}

fileread <- readLines("/cloud/project/PractExam/exampleFile.txt")

fileread

```


2B.
```{r}

commentvec <- fileread[grepl("//",fileread)]
commentvec

datavec <- fileread[grepl(";",fileread)]
datavec

```

3B.
```{r}


```
